---
name: Crystal Lewis
email: "cgh.lewis@gmail.com"
github: Cghlewis
www: cghlewis.com
date: "`r format(Sys.time(), '%B %Y')`"
output: vitae::awesomecv
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
```

#

\begin {center}
I am a researcher with over ten years of experience in project coordination and supervision, as well as data management, analysis, and reporting. I am happiest working at the intersection of K-12 education research and data management planning, helping researchers and practitioners obtain insights that improve student outcomes through harmonized, reliable, and documented data. I am also passionate about helping others organize their data and reporting through reproducible workflows.
\end{center}

# Technical Skills

R (data wrangling), R Markdown/Quarto (reporting), Qualtrics, Git and GitHub, SPSS, Microsoft Access, REDCap, FileMaker, Stata, Quick Base, SQL, SharePoint, Tableau

# Education

```{r}
library(tibble)
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where, ~details,
  "Master of Public Policy", "2009-2011", "University of Minnesota", "Minneapolis, MN", "Concentration: Advanced Policy Analysis",
  "Bachelor of Social Work", "2001-2005", "University of Missouri", "Columbia, MO", "Concentration: Research Methods"
) %>% 
  detailed_entries(Degree, Year, Institution, Where, details)
```

# Experience
```{r}
tribble(
  ~ role, ~ company, ~ loc, ~ dates, ~ details,
  "Data Management Consultant", "Freelance", "Remote", "Mar 2022 - Present", "Providing research data management consulting, training, and data wrangling services to improve organizational workflows.",
  "Data Scientist", "Streamline Data Science", "Remote", "Nov 2021 - Mar 2022", "Created example client facing customer relationship management dashboard in R flexdashboard to demonstrate services.",
  "Data Scientist", "Streamline Data Science", "Remote", "Nov 2021 - Mar 2022","Built Google Trends interactive R flexdashboard to show capabilities of automatic updating data.",
  "Director of Data Strategy", "Missouri Prevention Science Institute", "University of Missouri", "May 2019 - Nov 2021", "Strategized data management plans for over ten externally funded projects and oversaw their implementation.",
    "Director of Data Strategy", "Missouri Prevention Science Institute", "University of Missouri", "May 2019 - Nov 2021","Created standard operating procedures for all data management practices and provided annual staff training on systems.",
    "Director of Data Strategy", "Missouri Prevention Science Institute", "University of Missouri", "May 2019 - Nov 2021", "Merged, cleaned, queried, validated, and documented data collected from school districts, state education agencies, surveys, assessments, and observations using R.",
    "Director of Research Implementation","" ,"" , "Jul 2016-May 2019","Supervised project staff, ensuring successful completion of data collection activities for six federally funded randomized controlled trial studies and two county funded projects.", 
  "Director of Research Implementation","", "" , "Jul 2016-May 2019", "Designed and built data collection tools including Qualtrics surveys and Access tracking databases.",
  "Director of Research Implementation", "", "", "Jul 2016-May 2019", "Built reports, dashboards, and visualizations for dissemination of data.",
  "Research Associate","", "", "Aug 2013 - Jul 2016", "Coordinated activities for two Institute of Education Sciences funded randomized controlled trial studies.", 
  "Research Associate", "", "", "Aug 2013 - Jul 2016", "Collected data in schools through classroom observations, surveys, and assessments.", 
  "Research Associate", "", "", "Aug 2013 - Jul 2016","Established trusting relationships with school district partners.", 
  "Evaluation and Outcomes Manager", "Big Brothers Big Sisters of Eastern Missouri", "St. Louis, MO", "Jun 2011 - Aug 2013", "Oversaw the collection, analysis, and dissemination of data relating to performance management, outcomes, and stakeholder satisfaction.",
"Research Assistant", "Center for Advanced Studies in Child Welfare", "University of Minnesota", "Jan 2010 - Jul 2011", "Evaluated the effectiveness of the Hennepin County Attorney's Office truancy intervention program using qualitative and quantitative methods.", "Teaching Assistant", "Humphrey School of Public Affairs", "University of Minnesota", "Aug 2010 - Dec 2010", "Taught lab sessions of a graduate level introductory statistics course using Stata.", "Graduate Assistant", "Hennepin-University Partnership", "University of Minnesota", "Sep 2009 - May 2010", "Connected County officials with University faculty to develop effective partnerships to improve the community."
 ) %>% 
  detailed_entries(role, dates, company, loc, details)
```

# Service

```{r}
library(tibble)
tribble(
   ~ role, ~ company, ~ loc, ~ dates, ~ details,
   "Co-organizer", "POWER Issues in Data Management in Education Research Hub", "Remote", "Jan 2022 - Present", "Organize and host monthly meetups and presentations on data management topics for a group of researchers and data managers in the field of education.",
  "Co-organizer", "R-Ladies St. Louis", "St. Louis, MO", "Aug 2020 - Present", "Organize and host monthly workshops on programming in R.",
  "Advisory Committee Member", "Center for Open Science Unconference on Open Scholarship Practices in Education", "Remote", "Oct 2022 - Mar 2023", "Assisted in planning the 2023 event.",
  "Teaching Assistant", "RStudio Conference", "Washington D.C.", "July 2022", "Teaching Assistant for What They Forgot to Teach You About R Workshop.",
  "Teaching Assistant", "LaunchCode", "St. Louis, MO", "Jan 2018 - July 2018", "Developed curriculum and taught data analysis once a week for a cohort of 25 women looking to make a career transition.",
  "Team Lead", "AmeriCorps St. Louis Education Team", "St. Louis, MO", "Aug 2007 - Aug 2008", "Tutored elementary students, led educational programming, and supervised a team of three tutors."
) %>% 
  detailed_entries(role, dates, company, loc, details)
```


# Publications

Lewis, C. (2024). Data Management in Large-Scale Education Research. CRC Press. doi.org/10.1201/9781032622835

Cohen, D., Lewis, C.G., Eddy, C.L., Henry, L., Hodgson, C. & Huang, F.L. (2021) In-school and out-of-school suspension: Behavioral and psychological outcomes in a predominately black sample of middle school students. School Psychology Review, School Psychology Review, 52:1, 1-14.

Henry, L., Reinke, W.M., Herman, K.C., Thompson, A.M. & Lewis, C.G. (2020) Motivational 
interviewing with at-risk students (MARS) mentoring: Addressing the unique mental health needs of students in alternative school placements, School Psychology Review, 50:1, 62-74.

Huang, F., Lewis, C., Cohen, D., Prewett, S., & Herman, K. (2018). Bullying involvement, 
teacher-student relationships, and psychosocial outcomes. School Psychology Quarterly, 33(2), 223-234. 

Lewis, C.G., Herman, K.C., Huang, F.L., Stormont, M., Grossman, C., Eddy, C., & Reinke, 
W.M. (2017). The utility of single-item readiness screeners in middle school. Journal of School Psychology. 64, 1–16.


# Presentations

Lewis, C. (2025). Starting your Freelance Career. Guest presentation for Stanford University, Education Data Science seminar, Online.

Lewis, C. (2024). Data Management in Large-Scale Education Research. Presentation for the Center for Open Science, Online.

Lewis, C. (2024). Data Cleaning for Data Sharing Using R. Invited training for NCME Annual Meeting, Philadelphia, PA. 
Lewis, C. (2023). 10 Common Data Management Mistakes. Data Week, Alaska Region of Fish and Wildlife Service, Online. 

Lewis, C, Pileggi, S., and Higgins, P. (2023). Cleaning Medical Data in R. R/Medicine Conference, Online.

Lewis, C. (2023). Essential Data Management Best Practices and Tools for NIH Compliance Panel Discussion. Center for Open Science, Online.

Lewis, C. (2022). Data Management Workflows for Education Research Studies. Guest lecture given to a graduate research methods class at the University of Houston-Clear Lake, Online.

Lewis, C. (2022). 10 Common Data Management Mistakes. Presented for the Society for the Study of School Psychology, Early Career Foundation, Online.

Lewis, C. (2022). A Comparison of Packages to Generate Codebooks in R. A lightning talk for R-Ladies NYC, Online.

